Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/results_JCB.tex
added graphs results

>>>>

 \begin{figure}
\centering
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/5fold-a}
  \caption{$5-$fold coverage}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/10fold-a}
    \caption{$10-$fold coverage}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/15fold-a}
    \caption{$15-$fold coverage}
\end{subfigure}
\caption{Performance of error-correction over all positions. Subfigures show accuracy when
ART fold parameter is set to 5, 10 and $15-$fold coverage. We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values ranging of $\alpha = \{0, 0.5, 0.8, 1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance over at least 10 experiments.}

\label{fig:16s_all}
\end{figure}

 \begin{figure}
\centering
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/5fold-b}
  \caption{$5-$fold coverage}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/10fold-b}
    \caption{$10-$fold coverage}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/15fold-b}
    \caption{$15-$fold coverage}
\end{subfigure}
\caption{Performance of error-correction over positions inside a base pair. Subfigures show accuracy when
ART fold parameter is set to 5, 10 and $15-$fold coverage. We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values ranging of $\alpha = \{0, 0.5, 0.8, 1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance over at least 10 experiments.}
\label{fig:16s_bp}
\end{figure}
